07_summary_stats

### 2023-08-16 07_summary_stats.Rmd
made note about prelim results

Where are loudest sound levels?
```{r}
# For buoy 7
pct01_07 %>%
  summarise_if(is.numeric, list(~ min(., na.rm=TRUE)))

>>>>

Where are loudest sound levels? See @haver2020 for details on percentiles
5th percentile = exceeded most of the time, so refers to background sound
90th percentile = exceeded 10% of the time, so refers to PEAKS in sound level
Also see @haver2021 (fig 2) for daily TOL levels by site (can do by buoy)
```{r}
# For buoy 7
pct01_07 %>%
  summarise_if(is.numeric, list(~ min(., na.rm=TRUE)))
